---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {versionr} Package

<!-- badges: start -->
<!-- badges: end -->

{versionr} is a lightweight package designed to remove the friction of working
with version numbers in R. The main benefit of `versionr` is the 
[vctrs](https://vctrs.r-lib.org/)-powered S3 class `version_number`.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("wurli/versionr")
```
## Create Version Numbers

Version numbers can be created using characters or numeric vectors, and can
have arbitrary numbers of parts
```{r example}
library(versionr)

version_number("1.0.0", "1.0.1")
version_number(c(1, 0, 0, 0), c(1, 0, 0, 1))
```

## Sorting

A main benefit of {versionr} is easy version comparison and sorting
```{r}
nums <- version_number("1.0.0", "1.0.11", "1.0.2", "2.0.0.1")

# 1.0.11 should come after 1.0.2:
nums[2] > nums[3]

# Sorting is easy:
sort(nums)
```

## Bumping

Version numbers can be easily 'bumped' using `bump_version()`:
```{r}
bump_version(nums, "patch")
bump_version(nums, "major")
```


## Accessing Version Parts

Version numbers are vectors, and you can easily access particular parts using
`version_part()`:
```{r}
version_part(nums, "minor")
version_part(nums, "dev")
```

## Implementation

Behind the scenes, version numbers are just vectors of integers wrapped in a list:
```{r}
unclass(nums)
```
...This makes intuitive subsetting possible:
```{r}
nums[[3]][4]
```

