---
title: "Options"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Options}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

By default, {versionr} makes use of two options which can be adjusted depending
on your use-case.

## 1. `versionr.parts`
The default aliases for version parts are "major", "minor", "patch" and "dev". 
If you want to use different names, you can specify these using the `versionr.parts`
option. Functions which make use of these aliases are `bump_version()`, `version_part()`
and, notably, `tabulate_versions()`, which uses them as column names.

```{r setup}
library(versionr)

nums <- version_number("1.0.0", "1.0.0.1")

# Using the default alias for the fourth version part
tabulate_versions(nums)
version_part(nums, "dev")
```
```{r}
# Setting a custom alias 'fix' for the fourth part:
options(versionr.parts = c("major", "minor", "patch", "fix"))
tabulate_versions(nums)
version_part(nums, "fix")
```

## 2. `versionr.max_parts`
This is the maximum number of parts a version number will be allowed to have
on creation. If you try and sort a set of version numbers that includes
any with more than this number of parts, you will get an error. However, the 
default max number of parts is 6, which should be more than enough for most
uses. 

```{r}
long_versions <- version_number("1.0.0.0", "1.0.0.0.0.0.1")

# This will give an informative error
message(try(sort(long_versions), silent = TRUE))
```
```{r}
# Setting the option makes the error go away:
options(versionr.max_parts = 10)
sort(long_versions)
```

The need for this option is related to the way R handles sorting of S3 vectors: 
in order to compare two version numbers you need to have pre-knowledge of the 
length of both. So, before comparing them, `versionr` padds unspecified parts
with zeros so that all the numbers to compare have `versionr.max_parts` numbers
of parts.



